Incentivizing Exploration by Heterogeneous Users

### 2018-02-05 algorithm.tex
significant edits to algorithm section

\section{Algorithm and Upper Bound}
\label{sec:ub}

In this section, we propose a simple policy that mostly exploits, and occasionally incentivizes exploration when the probability of an arm would be pulled by all agent types below a time-varying threshold given the current posterior. We prove that with the help of heterogeneous preferences, we can get a certain amount of exploration for free via heterogeneity.

\subsection{Our Algorithm}
Our algorithm incentivizes pulling an arm $i$ at a time $t$ in round $n$ if and only if both of the following criteria are met:
\begin{itemize}
\item the probability of pulling arm $i$ would be below $n^{-1}$ without incentives; 
\item arm $i$ has not been played previously in the current round.
\end{itemize}
Ties are broken randomly.  This algorithm does not need to know the horizon $T$ in advance.

If our algorithm decides to incentivize an arm $i$, it uses the ``pay whatever it takes'' strategy in which the payment offered is $\max_{\theta,j} \theta \cdot (u_{j,t} - u_{i,t})$. This maximum over $\theta$ is taken over the support of $F$, which we recall is assumed compact.  (We use this ``pay whatever it takes'' strategy for its simplicity, and in Section~\ref{sec:pi} we provide an alternate and smaller incentive payment that achieves the same payment budget bound and regret bound).

We describe our algorithm in detail as follows:

\begin{algorithm}
\caption{Algorithm: Incentivizing Exploration}
\label{Alg1}
\begin{algorithmic}
\STATE Set n = 1 to denote the round number; Let $V=\emptyset$ be the set of arms that were pulled in the current round;
\FOR{ $t = 1, 2, 3, \cdots$}{
  \STATE Let $S = \{ i : P( \theta \cdot u_{i,t} > \theta \cdot u_{j,t}\ \forall j\ne i | u_{j,t}\ \forall j) < n^{-1}\}$ be the set of arms with unincentivized probability of being pulled below $n^{-1}$.
    \IF {$S\setminus V$ is non-empty}
  \STATE{Choose an arm $i$ uniformly at random from $S\setminus V$}
  \STATE{Pay whatever it takes to incentivize pulling arm $i$, i.e., offer payment 
    $c_{i,t} = \max_{\theta,j} \theta \cdot (u_{j,t} - u_{i,t})$ and $c_{j,t} = 0$ for $j \ne i$.}
  \ELSE
    \STATE {Let agents play myopically, i.e., offer payment $c_{j,t} = 0$ for all $j$}
  \ENDIF
    \STATE Denote $A_t$ as the pulled arm, update $V=V\cup\{A_t\}$, $u_{A_t,t}$ and $N(A_t,t)$
    \IF {$n\neq \min_{i}N(i,t)$} 
  \STATE $V=\emptyset$
    \ENDIF
    \STATE Update the round number, $n = \min_{i} N(i,t)$
}\ENDFOR

\end{algorithmic}
\end{algorithm}

@@

We use $R = \max_{\theta, i,j} \theta \cdot (u_i - u_j)$ to denote the
maximum regret that can be incurred at each time.
Assumption~\ref{A2} implies that the maximum regret or payment
incurred in any one round is finite.

@@

\subsection{General Results}

In this section, we prove Algorithm~\ref{Alg1} achieves $O(N^2+M(\log(T))^2)$ cumulative regret with $O(N^2)$ payment budget.  This is stated in the following pair of theorems, which together constitute our main results.

\begin{theorem}
The payment budget for Algorithm~\ref{Alg1} is bounded above by $O(N^2)$. 
\label{rst:budget}
\end{theorem}

\begin{theorem}
The cumulative regret for Algorithm~\ref{Alg1} is bounded above by $O(N^2 m + M m^2(\log(T))^2)$.
\label{rst:regret}
\end{theorem}

Before we prove these two theorems, we must first introduce two additional pieces of notation, which will be used in preliminary lemmas.  Let $S(\delta)$ be the proportion of users whose utility difference between their best and second best arm is less than $\delta$. Formally, $S(\delta)=P(\theta: \theta \cdot u_{B(\theta)}-\theta\cdot u_{\hat{B}(\theta)}\leq \delta)$. Then, let $p(\delta)=\min_{i}P(\{\theta:B(\theta)=i,\theta\cdot u_{B(\theta)}-\theta\cdot u_{\hat{B}(\theta)}>\delta\})$. We know $p(0)=p$.

@@

\begin{lemma}
$S(\delta)\leq M\delta$.
\label{lemma:sdelta}
\end{lemma}

\begin{proof}
\begin{align*}
S(\delta)&=\sum_{i,j}P(\theta\cdot(u_{i}-u_{j})\le \delta|\theta\in \Omega_{i,j})P(\theta\in \Omega_{i,j}) \\
&\leq \sum_{i,j}M\delta \times P(\theta\in \Omega_{i,j}) \\
&=M\delta.
\end{align*}
\end{proof}

The following lemma bounds the probability of making a mistake if we let the agents play myopically in the $n^{th}$ round, given that the utility difference between his/her best and second best arm is bounded below by a constant.

\begin{lemma}
Define $\tau$ to be any stopping time that is almost surely between $t_n$ and $t_{n+1}-1$ with respect to the filtration $\mathcal{F}_{t}=\sigma(A_1,\cdots,A_t,c_1,\cdots,c_t,O_1,\cdots,O_t)$, we have 
\begin{align}
P(\arg\max\{\theta_{\tau}\cdot u_{i,\tau}\}\neq B(\theta_{\tau})|\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})> 2Wm\lambda)\leq 24Nm\exp\left(-\frac{1.8n\lambda^2}{16\sigma^2}\right), \nonumber
\end{align}
for $n\geq n_{0}=\max\{50, \frac{92.16\sigma^4}{\lambda^4}\}$.
\label{round:prob}
\end{lemma}

We need the following lemma in order to prove Lemma~\ref{round:prob} and we include the proof in the appendix.

\begin{lemma}
For $n\geq n_{0}=\max\{50, \frac{92.16\sigma^4}{\lambda^4}\}$, we have
\begin{align}
\frac{n\lambda}{4\sigma}\geq \sqrt{0.6n\log(\log_{1.1}(n)+1)}. \nonumber
\end{align}
\label{n0-inequality}
\end{lemma}

To prove Lemma~\ref{round:prob}, we also need to use an adaptive concentration inequality due to \cite{zhao2016adaptive}. For reference, we state it here as a Lemma.

\begin{lemma}[Corollary 1 in \cite{zhao2016adaptive}]
Let $X_{i}$ be zero mean $1/2$-subgaussian random variables. $\{S_{n}=\sum_{i=1}^{n}X_{i},n\geq 1\}$ be a random walk. Let $J$ be any stopping time with respect to $\{X_1,X_2,\cdots\}$. We allow $J$ to take the value of $\infty$ where $P(J=\infty)=1-\lim_{n\rightarrow \infty}P(J\leq n)$. If
\begin{align}
f(n)=\sqrt{0.6n\log(\log_{1.1}(n)+1)+bn}, \nonumber
\end{align}
then
\begin{align}
Pr[\{S_{J}\geq f(J)\}\cap \{J<\infty\}]\leq 12e^{-1.8b}. \nonumber
\end{align}
\label{ACI-inequality}
\end{lemma}

We now prove Lemma~\ref{round:prob}.

\begin{proof}[Proof of Lemma~\ref{round:prob}]
In the $n^{th}$ round, we know all arms have been pulled at least $n$ times. For all the agents $\theta$ whose utility difference between their best and second best arm is greater than $2mW\lambda$, denote $K(\theta)=\max_{i\neq B(\theta)}\{\theta\cdot u_{i,t}\}$. If $|u_{i,t}^{j}-u_{i}^{j}|\leq \lambda$ for all $i,j$, then
\begin{align}
&\theta\cdot(u_{B(\theta),t}-u_{K(\theta),t}) \nonumber \\
\geq & \theta\cdot(u_{B(\theta),t}-u_{B(\theta)}) + \theta\cdot(u_{K(\theta)}-u_{K(\theta),t}) + \theta\cdot(u_{B(\theta)}-u_{K(\theta)}) \nonumber \\
> & -Wm\lambda - Wm\lambda + 2Wm\lambda = 0,\nonumber
\end{align}
which means their myopic action would incur no regret.

Define $\epsilon_{i,\tau}=u_{i,\tau}-u_i$ and $\epsilon_{i,\tau}^{j}$ to be the $j^{th}$ component of $\epsilon_{i,\tau}$. Thus, we have
\begin{align}
&P(\arg\max\{\theta_{\tau}\cdot u_{i,\tau}\}\neq B(\theta_{\tau})|\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})> 2Wm\lambda)\nonumber \\
\leq &P(\exists i, \exists j, |u_{i,\tau}^{j}-u_{i}^{j}|\geq\lambda |\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})> 2Wm\lambda) \nonumber \\
\leq & \sum_{i}\sum_{j} P(|u_{i,\tau}^{j}-u_{i}^{j}|\geq\lambda|\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})> 2Wm\lambda) \nonumber \\
= &  \sum_{i}\sum_{j} P(|\epsilon_{i,\tau}^{j}|\geq\lambda|\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})> 2Wm\lambda). \label{ACI}
\end{align}

To bound equation~(\ref{ACI}), we use Lemma~\ref{ACI-inequality}. Define
\begin{align}
S_{N(i,\tau)}^{i,j}=\frac{\epsilon_{i,\tau}^{j}}{2\sigma}. \nonumber
\end{align}

Based on Lemma~\ref{n0-inequality}, for $n_{0}=\max\{50,\frac{92.16\sigma^2}{\lambda^2}\}$ and $n\geq n_{0}$, we have
\begin{align}
\frac{n\lambda}{4\sigma}\geq \sqrt{0.6n\log(\log_{1.1}(n)+1)}. \nonumber
\end{align}

Thus, if we set $b=\frac{n\lambda^2}{16\sigma^2}$ in Lemma~\ref{ACI-inequality}, for any $N(i,\tau)\geq n\geq n_{0}$, we have
\begin{align}
\frac{N(i,\tau)\lambda}{2\sigma}\geq & \sqrt{0.6N(i,\tau)\log(\log_{1.1}(N(i,\tau))+1)}+\frac{\lambda}{4\sigma}\sqrt{n N(i,\tau)} \nonumber \\
\geq & \sqrt{0.6N(i,\tau)\log(\log_{1.1}(N(i,\tau))+1)+bN(i,\tau)}, \nonumber 
\end{align}
where the last inequality is because $\sqrt{x}+\sqrt{y}\geq \sqrt{x+y}$. Thus, we have
\begin{align}
&P(\epsilon_{i,\tau}^{j}\geq\lambda|\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})> 2Wm\lambda) \nonumber \\
=&P\left(S_{N(i,\tau)}^{i,j}\geq \frac{N(i,\tau)\lambda}{2\sigma}\bigg|\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})> 2Wm\lambda\right) \nonumber \\
\leq & P\left(S_{N(i,\tau)}^{i,j}\geq \sqrt{0.6 N_{i,\tau}\log(\log_{1.1}(N(i,\tau))+1)+b N(i,\tau)}\bigg|\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})> 2Wm\lambda\right) \nonumber \\
\leq & 12\exp( -1.8b) = 12\exp\left(\frac{-1.8 n\lambda^2}{16\sigma^2}\right). \nonumber
\end{align}
Similarily, we can bound 
\begin{align}
&P(\epsilon_{i,\tau}^{j}\leq-\lambda|\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})> 2Wm\lambda) \nonumber \\
=&P(-\epsilon_{i,\tau}^{j}\geq \lambda|\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})> 2Wm\lambda) \nonumber \\
\leq & 12\exp\left(\frac{-1.8 n\lambda^2}{16\sigma^2}\right). \nonumber 
\end{align}

Therefore, we know $P(|\epsilon_{i,\tau}^{j}|\geq \lambda|\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})> 2Wm\lambda)\leq 24\exp\left(\frac{-1.8 n\lambda^2}{16\sigma^2}\right)$. Thus, we know
\begin{align}
&\sum_{i}\sum_{j} P(|\epsilon_{i,\tau}^{j}|\geq \lambda|\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})> 2Wm\lambda)  \nonumber \\
\leq& 24Nm \exp\left(\frac{-1.8 n\lambda^2}{16\sigma^2}\right). \nonumber
\end{align}
\end{proof}

Before we start analyzing the cumulative regret, we first prove the following lemma which bounds the expected length of each round.
\begin{lemma}
Using our algorithm, we have $\mathbb{E}[t_{n+1}-t_{n}]\leq Nn$, $\forall n\geq 1$.
\label{round:length}
\end{lemma}
\begin{proof}
A round completes when each arm is pulled at least once in that round. Let $X_{i}$ be the number of agents who come to the system between the time after the $(i-1)^{th}$ unique arm was pulled, up to and including the time when the $i^{th}$ unique arm was pulled. Then we know 
\begin{equation*}
\mathbb{E}[t_{n+1}-t_{n}]=\sum_{i=1}^{N}E[X_{i}].
\end{equation*}

Fix $i$. In bounding $X_i$, we think of agents as ``trials'', where each trial can result in a new unique arm being pulled (which we call a ``successful'' trial), or not.  There are two ways a trial can be successful:
\begin{itemize}
\item If there is at least one arm that has not been pulled and the probability of an agent utility function that would pull this arm without incentives is less than $n^{-1}$, then the principal will offer an incentive that causes this arm to be pulled (or one of these arms if there is more than one). In this case, the probability that the trial is succesful is $1$.  
\item The probability of an agent utility function that would pull each un-pulled arm without incentives is at least $n^{-1}$. In this case, the probability that the trial is successful is at least $n^{-1}$.
\end{itemize}

Thus, $X_{i}$ is stochastically dominated below by a geometric random variable with success probability $n^{-1}$, the expected number of trials up to and including the first success, $E[X_i]$, is bounded above by $n$.  Thus,
\begin{align}
E[t_{n+1}-t_{n}]\leq Nn. \nonumber
\end{align}
\end{proof}

Using the above lemmas, we are ready to prove Theorem~\ref{rst:budget}. We include the proof of Theorem~\ref{rst:budget} in the appendix. Below, we bound the expected number of payments for our algorithm.
\begin{lemma}
The expected number of payments for Algorithm~\ref{Alg1} is bounded above by $O(N^2)$.
\label{lemma:numP}
\end{lemma}
\begin{proof}
If $|u_{i}^{j}-u_{i,t}^{j}|\leq \lambda$ is true $\forall i$, $\forall j$, then we know for those $\theta\in \{\theta:\theta\cdot u_{B(\theta)}-\max_{j\neq B(\theta)}\{\theta \cdot u_{j}\}> 2mW\lambda\}$, they will correctly identify their best arm. Thus we know, in the $n^{th}$ round, if $|u_{i}^{j}-u_{i,t}^{j}|\leq \frac{p^{-1}(\frac{p}{2})}{2Wm}$ $\forall i$ and $\forall j$, and $n^{-1}\leq p/2$, we do not need to incentivize any arms. In order to have $n^{-1}\leq \frac{p}{2}$, we need $n\geq \frac{2}{p}$. Denote $n_1=\max\{n_{0}, \frac{2}{p}\}$. Denote $\delta_{0}=p^{-1}(\frac{p}{2})>0$ (because of Assumption~\ref{A1}).

>>>>

% move to colt.tex eventually

\newcommand{\e}{\mathrm{e}}
\providecommand{\Kth}[1]{\ensuremath{{#1}^{\rm th}}}

\def\QED{{\phantom{x}} \hfill \ensuremath{\rule{1.3ex}{1.3ex}}}

\newcommand{\extraproof}[1]{\rm \trivlist \item[\hskip \labelsep{\bf Proof of #1. }]}
\def\endextraproof{\QED \endtrivlist}

\def\emptyproof{\rm \trivlist \item[\hskip \labelsep{\bf Proof. }]}
\def\endemptyproof{\endtrivlist}

\section{Main Algorithm and Analysis}
\label{sec:ub}

The algorithm achieving the claimed bounds of
Theorem~\ref{thm:main-overview} is fairly simple.
It mostly allows agents to exploits, but when an arm is estimated to
be extremely unlikely to be pulled by any agents,
the algorithm incentivizes such an arm with a payment that is so high
that the next agent is guaranteed to pull the arm.
This way, the algorithm ensures that each arm is pulled at least a
certain minimum number of times.

More precisely, the algorithm divides time into \emph{phases}
$s = 1, 2, 3, \ldots$.
Phase $s$ ends when each arm has been pulled at least $s$ times.
An arm $i$ is \emph{payment-eligible} at time $t$ (in phase $s$)
if both of the following hold:

\begin{itemize}
\item $i$ has been pulled at most%
\footnote{in fact: exactly, since the algorithm entered phase $s$}
$s-1$ times up to time $t$, i.e., $\NumPull{t}{s} \leq s-1$.
\item Based on the current estimates \ArmEV{t}{i'} of all arms'
attribute vectors, the probability of pulling arm $i$ is less than $1/s$.
Let $\PullProb{t}{i} = \Prob[\AgV \sim \AgentDist]{\AgV \cdot \ArmEV{t}{i} > \AgV
  \cdot \ArmEV{t}{i'} \mbox{ for all } i' \neq i}$
be the probability that arm $i$ will be pulled
by the next (random) agent based on the current estimates. 
Then, the second criterion for payment-eligibility is that
$\PullProb{t}{i} < 1/s$.
\end{itemize}

When multiple arms are payment-eligible, the algorithm picks one
uniformly at random to incentivize.
When the algorithm decides to incentivize an arm $i$,
it offers ``whatever it takes,'' i.e., offers a payment of
$\Pay{t}{i} = \max_{\AgV,i'} \AgV \cdot (\ArmEV{t}{i'} - \ArmEV{t}{i})$.
The maximum for \AgV is taken over the support of \AgentDist;
recall that we assumed this support to be compact.
The payment \Pay{t}{i} may appear unnecessarily high.
Indeed, we show in Section~\ref{sec:pi} that it suffices to
incentivize only a $1/s$ fraction of the agents.
\dkcomment{Given that we don't prove anything there, is ``show'' the
  right word?}
Here, we focus on the higher payments for simplicity of analysis.

Notice that \PullProb{t}{i} depends on the estimates for \emph{all}
arms; thus, by pulling some other arm $i'$, an arm $i$ may become
payment-eligible, or cease to be so.
Algorithm~\ref{alg:basic-incentivizing} gives the full details.

\begin{algorithm}
\caption{Algorithm: Incentivizing Exploration \label{alg:basic-incentivizing}}
\begin{algorithmic}
\STATE Set the current phase number $s = 1$.
\FOR{time steps $t = 1, 2, 3, \ldots$}
\IF{$\NumPull{t}{i} \geq s$ for all arms $i$}
\STATE Increment the phase $s = s + 1$.
\ENDIF
\IF{there is a payment-eligible arm $i$}
\STATE Let $i$ be a uniformly random payment-eligible arm.
\STATE Offer payment
$\Pay{t}{i} = \max_{\AgV,i'} \AgV \cdot (\ArmEV{t}{i'} - \ArmEV{t}{i})$
for pulling arm $i$
(and payment 0 for all other arms).
\ELSE
\STATE Let agent $t$ play myopically, i.e., offer payments 0 for all arms.
\ENDIF
\ENDFOR
\end{algorithmic}
\end{algorithm}

The high-level idea of the proof of Theorem~\ref{thm:main-overview}
is the following.
Because the algorithm ensures that each arm is pulled
``frequently enough,''
the estimates \ArmEV{t}{i} become exponentially more accurate in the
phase number $s$.
Thus, the fraction of agents who misidentify their best arm decreases
exponentially as well.
Because for each arm, enough agents have a true preference for this
arm, once the arms' attribute vectors are learned well enough,
the algorithm will not need to incentivize any arm pulls any more,
resulting in a payment bound independent of $T$.
Similarly, the regret will decrease exponentially, and mostly accrue
due to agents close to the border making mistakes in their arm choices.
The detailed analysis following this outline is somewhat subtle, though,
due to the dependencies between the agents' arm pulls and the
estimates which in turn are based on past arm pulls.
We begin with several technical lemmas that are used for both the
payment and regret bounds.

To capture the probability masses of problematic and non-problematic
agents, we define the following:
$\AlmostTied{\delta} = \Prob[\AgV \sim \AgentDist]{%
\AgV \cdot (\ArmV{\Best{\AgV}} - \ArmV{\Second{\AgV}}) \leq \delta}$
is the total probability mass (across all arms) of agents
whose (actual) preference for their best arm over their second-best
arm is at most $\delta$.
The minimum probability mass of users who prefer their best arm
sufficiently strongly over their second-best arm is denoted by
$\ClearPref{\delta} = \min_{i}
\Prob[\AgV \sim \AgentDist]{\Best{\AgV}=i,%
\AgV \cdot (\ArmV{\Best{\AgV}} - \ArmV{\Second{\AgV}}) > \delta}$.
Notice that while \AlmostTied{\delta} (being a measure of problematic
agents) is defined as a sum over all arms,
while  \ClearPref{\delta} (being a measure of non-problematic agents)
is defined as a minimum over arms.
Also notice that $\ClearPref{0} = \MinProb$.
\dkcomment{We should stress somewhere that we assume that actual ties
  have measure 0.}

@@

We use $R = \max_{\AgV, i,j} \AgV \cdot (u_i - u_j)$ to denote the
maximum regret that can be incurred at each time.
Assumption~\ref{A2} implies that the maximum regret or payment
incurred in any one round is finite.

@@

In this section, we prove Algorithm~\ref{alg:basic-incentivizing} achieves $O(\ARMNUM^2+\TieDensity(\log(T))^2)$ cumulative regret with $O(\ARMNUM^2)$ payment budget.  This is stated in the following pair of theorems, which together constitute our main results.

\begin{theorem}
The payment budget for Algorithm~\ref{alg:basic-incentivizing} is bounded above by $O(\ARMNUM^2)$. 
\label{rst:budget}
\end{theorem}

\begin{theorem}
The cumulative regret for Algorithm~\ref{alg:basic-incentivizing}
is bounded above by $O(\ARMNUM^2 d + \TieDensity d^2(\log(T))^2)$.
\label{rst:regret}
\end{theorem}

@@

Notation: $t_s$ is end time for phase $s$.

\subsection{General Lemmas}

We begin by showing that under our assumptions, the measure of
problematic arms cannot be too large.

\begin{lemma} \label{lem:sdelta}
$\AlmostTied{\delta} \leq \TieDensity \cdot \delta$ for all $\delta$.
\end{lemma}

\begin{emptyproof}
Using the upper bound from Assumption~\ref{A1}, we can bound

\begin{align*}
\AlmostTied{\delta}
& = \sum_{i,i'} \ProbC{\AgV \cdot (\ArmV{i} - \ArmV{i'}) \leq \delta}%
    {\AgV \in \FirstTwo{i}{i'}}
  \cdot \Prob{\AgV \in \FirstTwo{i}{i'}}\\
& \leq \sum_{i,i'} \TieDensity \cdot \delta
    \cdot \Prob{\AgV \in \FirstTwo{i}{i'}}
\; = \; \TieDensity \cdot \delta. \QED
\end{align*}
\end{emptyproof}

We next bound the length of any phase, which will be useful to bound
the cumulative regret of the early rounds
(before tail bounds have kicked in).

\begin{lemma} \label{lem:phase-length}
For any $s$, the expected length of phase $s$ is at most
$\ARMNUM \cdot s$ time steps.
\end{lemma}

\begin{proof}
Let $S$ be the set of arms that have been pulled at most
$s-1$ times at the start of phase $s$.
Thus, phase $s$ ends when each $i \in S$ has been pulled at least once.
Consider any time step $t$.
If $S$ contains at least one payment-eligible arm $i$,
then some payment-eligible arm will be pulled with probability 1,
and every payment-eligible arm is in $S$.
In particular, the size of $S$ decreases with probability 1.
If $S$ contains no payment-eligible arm,
then by definition of payment-eligibility,
each arm $i \in S$ has probability at least $1/s$ of being pulled.
In particular, the size of $S$ decreases with probability at least $1/s$.

In either case, the expected number of time steps until
$|S|$ decreases is at most $s$,
so the expected number of steps until $S$ is empty is at most
$\ARMNUM \cdot s$.
\dkcomment{If we wanted, this bound could probably be improved using a
  coupon collector argument. But it would look uglier.}
\end{proof}

The key technical lemma bounds the probability of mistakes in myopic play.
Intuitively, because estimates of the arms' attribute vectors become
exponentially more accurate with increasing phases $s$,
errors from myopic play should decrease exponentially.
That intuition is captured by the following lemma.

\begin{lemma} \label{lem:round-prob}
Let $x > 0$ be arbitrary.
Recall that $\sigma$ is the standard deviation of the Gaussian noise.
Let $\LatePhase \geq \max \SET{50, \frac{92.16 \sigma^4}{x^4}}$.

\dkcomment{Is it problematic that we use $\sigma$ for two things here?}
Let $\tau$ be any stopping time that is almost surely \dkcomment{What
  exactly do we mean by this here?} in phase $s$,
with respect to the filtration
$\mathcal{F}_{t} = \sigma (\Pull{1}, \ldots, \Pull{t},
                          \PayA{1}, \ldots, \PayA{t},
                          \ObsV{1}, \ldots, \ObsV{t})$.
Then, for all $s \geq \LatePhase$,
\begin{align*}
  \ProbC[\AgV \sim \AgentDist]{%
  \argmax \SET{\AgentV{\tau} \cdot \ArmEV{\tau}{i}} \neq \Best{\AgentV{\tau}}}{%
  \AgentV{\tau} \cdot (\ArmV{\Best{\AgentV{\tau}}} - \ArmV{\Second{\AgentV{\tau}}})
  > 2\Diam d x}
& \leq 24 \ARMNUM d \exp\left(-\frac{1.8 s x^2}{16 \sigma^2} \right).
\end{align*}
\end{lemma}

The proof of Lemma~\ref{lem:round-prob} is based on an adaptive
concentration inequality due to \cite{zhao2016adaptive},
given as Lemma~\ref{lem:ACI-inequality}.

\begin{lemma}[Corollary 1 of \cite{zhao2016adaptive}]
\label{lem:ACI-inequality}
Let $X_i$ be zero-mean $1/2$-subgaussian random variables,
and $\SET{S_n = \sum_{i=1}^n X_i, n \geq 1}$ the corresponding random walk.
Let $J$ be any stopping time with respect to $\SET{X_1, X_2, \ldots}$.
(We allow $J$ to take the value $\infty$,
defining $\Prob{J = \infty} = 1 - \lim_{n \to \infty} \Prob{J \leq n}$.)
Define \dkcomment{I'm making the dependence of $b$ on $n$ explicit,
  since that's how we're using it.}
\begin{align*}
g(n) & = \sqrt{0.6 n \cdot \log (\log_{1.1}(n) + 1) + n \cdot b(n)}.
\end{align*}
Then, 
\begin{align*}
\Prob{J < \infty \mbox{ and } S_J \geq g(J)} \leq 12 \e^{-1.8 b(n)}.
\end{align*}
\end{lemma}

\begin{extraproof}{Lemma~\ref{lem:round-prob}}
Consider any agent type \AgentV{\tau} at the (random) time $\tau$ such that
$\AgentV{\tau} \cdot (\ArmV{\Best{\AgentV{\tau}}} - \ArmV{\Second{\AgentV{\tau}}})
> 2\Diam d x$.
We will use Lemma~\ref{lem:ACI-inequality} to show that
for any arm $i$ and attribute $j = 1, \ldots, d$,
with probability at least
$1 - 24 \exp \left( \frac{-1.8 s x^2}{16\sigma^2} \right)$,
the estimated attribute $j$ for arm $i$ is close enough to the true attribute: 
$|\ArmE{\tau}{i}{j} - \Arm{i}{j}| \leq x$.
By a union bound over all $i, j$, this bound holds simultaneously for all
arms and coordinates with probability at least
$1 - 24 \ARMNUM d \cdot \exp \left( \frac{-1.8 s x^2}{16\sigma^2} \right)$.

Then, consider any type $\AgV = \AgentV{\tau}$ in the high-probability event,
and let $i \neq \Best{\AgentV{\tau}}$ be any other arm.
By the conditioning of \AgentV{\tau}, the true reward from arm $i$ is
much smaller than from the best arm:
$\AgV \cdot (\ArmV{\Best{\AgV}} - \ArmV{i}) > 2\Diam d x$.
Because each coordinate of \ArmEV{\tau}{\Best{\AgV}} and of
\ArmEV{\tau}{i} is estimated accurately to within $x$, 
we get that 
$\AgV \cdot (\ArmEV{\tau}{\Best{\AgV}} - \ArmV{\Best{\AgV}})
\geq - \Diam d x$
and
$\AgV \cdot (\ArmEV{\tau}{i} - \ArmV{i}) \leq \Diam d x$.
Hence,

\begin{align*}
\AgV \cdot (\ArmEV{\tau}{\Best{\AgV}} - \ArmEV{\tau}{i})
& =
\AgV \cdot (\ArmEV{\tau}{\Best{\AgV}} - \ArmV{\Best{\AgV}})
+ \AgV \cdot (\ArmV{\Best{\AgV}} - \ArmV{i})
+ \AgV \cdot (\ArmV{i} - \ArmEV{\tau}{i})\\
& > -\Diam d x + 2 \Diam d x - \Diam d x
\; = \; 0,
\end{align*}
which means that the agent with type \AgV will in fact choose
the optimal arm in the high-probability event.

It remains to prove that with high probability, all arms' coordinates
are estimated sufficiently accurately for type \AgentV{\tau}.
Thereto, fix an arm $i$ and attribute $j$.
For any $n \geq 1$, let $k_s$ be the time step right after arm $i$ has
been pulled for the \Kth{n} time.
\dkcomment{I'm writing $n$ instead of $s$ here because $S_s$ would
  look ugly, and $n$ is consistent with the lemma.
  Or we could rename $S$ to something else.}
Define
$S_n := \frac{n \cdot (\ArmE{k_n}{i}{j} - \Arm{i}{j})}{2 \sigma}$
to be the sum of all attribute-$j$ noise components up to and
including the \Kth{n} pull of arm $i$,
\dkcomment{I'm not sure if we have defined the notation for components
  of vectors in the \emph{superscript}. Let's make sure not to forget it.}
renormalized to have standard deviation $1/2$.
\dkcomment{Is this the correct scaling.}
The $S_n$ define an unbiased half-subgaussian random walk,
and we can therefore apply Lemma~\ref{lem:ACI-inequality} to them.
Specifically, we set $b(n) = \frac{n x^2}{16 \sigma^2}$,
and obtain that

\begin{align*}
\Prob{J < \infty \mbox{ and } S_J \geq 
\sqrt{0.6 J \cdot \log (\log_{1.1}(J) + 1) + \frac{J^2 x^2}{16 \sigma^2}}}
& \leq 12 \exp \left( \frac{-1.8 J x^2}{16 \sigma^2} \right).
\end{align*}

Applying Lemma~\ref{lem:ACI-inequality} to $-S_n$ with the same choice
of $b(n)$, and taking a union bound over both cases, we obtain that

\begin{align*}
\Prob{J < \infty \mbox{ and } |S_J| \geq 
\sqrt{0.6 J \cdot \log (\log_{1.1}(J) + 1) + \frac{J^2 x^2}{16 \sigma^2}}}
& \leq 24 \exp \left( \frac{-1.8 J x^2}{16 \sigma^2} \right).
\end{align*}

In the high-probability case
$|S_J| \leq
\sqrt{0.6 J \cdot \log (\log_{1.1}(J) + 1) + \frac{J^2 x^2}{16 \sigma^2}}$,
we first use that $\sqrt{\cdot}$ is sublinear to bound
$\sqrt{0.6 J \cdot \log (\log_{1.1}(J) + 1) + \frac{J^2 x^2}{16 \sigma^2}}
\leq \sqrt{0.6 J \cdot \log (\log_{1.1}(J) + 1)} + \frac{J x}{4 \sigma}$.
Then, we use the following technical Lemma~\ref{lem:n0-inequality}
(whose proof is given in the appendix, and whose precondition we verify
momentarily) to bound the first term,
giving us an overall upper bound of
$|S_J| \leq \frac{J x}{2 \sigma}$.

\begin{lemma} \label{lem:n0-inequality}
For any $n \geq \LatePhase = \max (50, \frac{92.16 \sigma^4}{x^4})$, 
\begin{align*}
\sqrt{0.6 n \log (\log_{1.1}(n) + 1)} & \leq \frac{n x}{4 \sigma}. 
\end{align*}
\end{lemma}

Substituting the definition of $S_J$ and canceling common terms,
the inequality implies that
$|\ArmE{k_J}{i}{j} - \Arm{i}{j}| \leq x$.
By the assumptions of the lemma,
the stopping time $\tau$ is such that almost surely, each arm --- and
in particular arm $i$ --- has been pulled at least
$s \geq \LatePhase$ times at time $\tau$.
Defining $J$ to be the number of times that $i$ has been pulled at
time $\tau$, we obtain that $J$ satisfies the precondition of
Lemma~\ref{lem:n0-inequality}.
Furthermore, with probability 1, $J$ will be finite, meaning that
\begin{align*}
& \Prob{S_J \geq 
\sqrt{0.6 J \cdot \log (\log_{1.1}(J) + 1) + \frac{J^2 x^2}{16
    \sigma^2}}}\\
= & \Prob{J < \infty \mbox{ and } S_J \geq 
\sqrt{0.6 J \cdot \log (\log_{1.1}(J) + 1) + \frac{J^2 x^2}{16
    \sigma^2}}}.
\end{align*}

Finally, this choice of $J$ ensures that
$\ArmE{k_J}{i}{j} = \ArmE{\tau}{i}{j}$,
and we have thus shown that
$|\ArmE{\tau}{i}{j} - \Arm{i}{j}| \leq x$ for all $i,j$.
\end{extraproof}

\subsection{Bounding the Total Payment}
